GeneSet_Expansion

### 2020-05-16 code/Jansen_SMR.Rmd
Jansen SMR

system( 'awk \'{print $1"\t"$2"\t"$3"\t"$4"\t"$5"\t"$6"\t"$7"\t"$8"\t"$9"\t"$10"\t"$11"\t"$12"\t"$13"\t"$14"\t"$15"\t"$16"\t"$17"\t"$18"\t"$19"\t"$20"\t"$21"\t"$22}\' Compiled_SMR.tsv > temp.tsv') 
system('mv temp.tsv Compiled_SMR.tsv')
Table<-read.table(file='Compiled_SMR.tsv', , sep='\t', header=T)
system( 'awk -F \',\' \'{ print $5"\t"$6 }\' Cortex_MetaAnalysis_ROSMAP_CMC_HBCC_Mayo_cis_eQTL_release.csv | sort | uniq | grep -v \'geneSymbol\' > Translate.txt')
Trans <- read.table( file='Translate.txt', sep ="\t", header=F)
row.names(Trans) <- Trans$V1
Trans$V1 <- as.character(Trans$V1) 
Trans$V2 <- as.character(Trans$V2) 
Trans[ is.na(Trans$V2), ]$V2 <- Trans[ is.na(Trans$V2), ]$V1
Trans[ Trans$V2 == "", ]$V2 <- Trans[ Trans$V2 == "", ]$V1
Table$Gene <- as.character(Table$Gene)
Table$probeID <- as.character(Table$probeID)
Table$Gene <- Trans[Table$probeID,]$V2
write.table(Table, file='Final_SMR_TWAS_Jansen_Validation.tsv', row.names=F, col.names=T, quote=F, sep ='\t')
```

@@

```{r knitmd, eval=FALSE, cache=FALSE, include=FALSE}
reticulate::use_python("/usr/bin/python", required = TRUE)
synapseclient <- reticulate::import("synapseclient")
syn_temp <- synapseclient$Synapse()
syn_temp$login()
setwd("~/TWAS/code/")
source("~/TWAS/utilityFunctions/knitfile2synapseClient.R")
source("~/TWAS/utilityFunctions/hook_synapseMdSyntax_plot.R")
createAndKnitToFolderEntityClient(file = "Jansen_SMR.Rmd",
                                  parentId ="syn22050453",
                                  folderName = 'Summary-data-based Mendelian Randomization')
```

>>>>

#system( 'awk \'{print $1"\t"$2"\t"$3"\t"$4"\t"$5"\t"$6"\t"$7"\t"$8"\t"$9"\t"$10"\t"$11"\t"$12"\t"$13"\t"$14"\t"$15"\t"$16"\t"$17"\t"$18"\t"$19"\t"$20"\t"$21"\t"$22}\' Compiled_SMR.tsv > temp.tsv') 
#system('mv temp.tsv Compiled_SMR.tsv')
Table<-read.table(file='Compiled_SMR.tsv', , sep='\t', header=T)
system( 'awk -F \',\' \'{ print $5"\t"$6 }\' Cortex_MetaAnalysis_ROSMAP_CMC_HBCC_Mayo_cis_eQTL_release.csv | sort | uniq | grep -v \'geneSymbol\' > Translate.txt')
Trans <- read.table( file='Translate.txt', sep ="\t", header=F)
row.names(Trans) <- Trans$V1
Trans$V1 <- as.character(Trans$V1) 
Trans$V2 <- as.character(Trans$V2) 
Trans[ is.na(Trans$V2), ]$V2 <- Trans[ is.na(Trans$V2), ]$V1
Trans[ Trans$V2 == "", ]$V2 <- Trans[ Trans$V2 == "", ]$V1
Table$Gene <- as.character(Table$Gene)
Table$probeID <- as.character(Table$probeID)
Table$Gene <- Trans[Table$probeID,]$V2
write.table(Table, file='Final_SMR_TWAS_Jansen_Validation.tsv', row.names=F, col.names=T, quote=F, sep ='\t')
```

@@

```{r knitmd, eval=FALSE, cache=FALSE, include=FALSE}
reticulate::use_python("/usr/bin/python", required = TRUE)
synapseclient <- reticulate::import("synapseclient")
syn_temp <- synapseclient$Synapse()
syn_temp$login()
setwd("~/TWAS/code/")
source("~/TWAS/utilityFunctions/knitfile2synapseClient.R")
source("~/TWAS/utilityFunctions/hook_synapseMdSyntax_plot.R")
createAndKnitToFolderEntityClient(file = "Jansen_SMR.Rmd",
                                  parentId ="syn22050453",
                                  folderName = 'Jansen_SMR')
```
